Variability in upwelling patterns across the Benguela upwelling systems

### 2019-10-08 Write_up/Paper1_writeup.Rmd
updated

<!-- \def\tiny{\@setfontsize\tiny{10pt}{11pt}} -->
\begin{tiny}
\begin{center}
\setlength\tabcolsep{3pt}
\begin{longtable}{|r|r|p{2cm}|}
\caption{The absolute cumulative intensity (°C.day) for the sites located within the Benguela upwelling system using the OISST dataset. The site column gives the name of the site. The distance column gives the distance from the coastline as seen in Fig 1. The cumulative intensity expects as absolute magnitudes rather than relative seasonal climatology} \\

@@

Lamberts Bay & 10000 & 5.47875 \\
Lamberts Bay & 20000 & 5.47875 \\
Lamberts Bay & 30000 & 7.67025 \\
Lamberts Bay & 40000 & 1.09575 \\
Lamberts Bay & 50000 & -8.76600 \\
Port Nolloth & 10000 & 0.36525  \\
Port Nolloth & 20000 & -3.28725 \\
Port Nolloth & 30000 & -2.92200 \\
Port Nolloth & 40000 & -3.65250 \\
Port Nolloth & 50000 & -3.28725 \\
Saldanha Bay & 10000 & -0.73050 \\
Saldanha Bay & 20000 & -0.36525 \\
Saldanha Bay & 30000 & -4.38300 \\
Saldanha Bay & 40000 & -10.22700 \\
Saldanha Bay & 50000 & -12.41850 \\
Sea Point & 10000 & -8.76600  \\
Sea Point & 20000 & -3.65250 \\
Sea Point & 30000 & -1.46100 \\
Sea Point & 40000 & -9.49650 \\
Sea Point & 50000 & -18.62775 \\

@@

<!-- \def\tiny{\@setfontsize\tiny{10pt}{11pt}} -->
\begin{tiny}
\begin{center}
\setlength\tabcolsep{3pt}
\begin{longtable}{|r|r|p{2cm}|}
\caption{The absolute cumulative intensity (°C.day) for the sites located within the Benguela upwelling system using the CMC dataset. The site column gives the name of the site. The distance column gives the distance from the coastline as seen in Fig 1. The cumulative intensity expects as absolute magnitudes rather than relative seasonal climatology} \\

@@

Lamberts Bay & 10000 & -26.29800 \\
Lamberts Bay & 20000 & -25.56750 \\
Lamberts Bay & 30000 & -23.74125 \\
Lamberts Bay & 40000 & -31.41150 \\
Lamberts Bay & 50000 & -31.77675 \\
Port Nolloth & 10000 & -15.34050 \\
Port Nolloth & 20000 & -16.43625 \\
Port Nolloth & 30000 & -15.70575 \\
Port Nolloth & 40000 & -20.45400 \\
Port Nolloth & 50000 & -24.83700 \\
Saldanha Bay & 10000 & -29.58525 \\
Saldanha Bay & 20000 & -36.52500 \\
Saldanha Bay & 30000 & -42.73425 \\
Saldanha Bay & 40000 & -46.38675 \\
Saldanha Bay & 50000 & -45.29100 \\
Sea Point & 10000 & -28.48950 \\
Sea Point & 20000 & -30.31575 \\
Sea Point & 30000 & -36.89025 \\
Sea Point & 40000 & -38.35125 \\
Sea Point & 50000 & -37.25550 \\

@@

Lamberts Bay & -1.46100 \\
Port Nolloth & -3.65250 \\
Saldanha Bay & -2.55675 \\
Sea Point & -10.95750 \\

>>>>

<!-- \def\tiny{\@setfontsize\tiny{10pt}{11pt}} -->
\begin{tiny}
\begin{center}
\setlength\tabcolsep{3pt}
\begin{longtable}{|r|r|p{2cm}|}
\caption{The cumulative intensity (°C x days) for the sites located within the Benguela upwelling system using the OISST dataset. The site column gives the name of the site. The distance column gives the distance from the coastline as seen in Fig 1.} \\

@@

Lamberts Bay & 10000 & -1.83 \\
Lamberts Bay & 20000 & -1.83 \\
Lamberts Bay & 30000 & -1.83 \\
Lamberts Bay & 40000 & -0.73 \\
Lamberts Bay & 50000 & 0.73 \\
Port Nolloth & 10000 & -1.10 \\
Port Nolloth & 20000 & -0.37 \\
Port Nolloth & 30000 & 0.00 \\
Port Nolloth & 40000 & 0.37 \\
Port Nolloth & 50000 & 0.37 \\
Saldanha Bay & 10000 & -2.19 \\
Saldanha Bay & 20000 & -1.83 \\
Saldanha Bay & 30000 & -0.73 \\
Saldanha Bay & 40000 & 0.73 \\
Saldanha Bay & 50000 & 1.10\\
Sea Point & 10000 & -2.56 \\
Sea Point & 20000 & -3.29 \\
Sea Point & 30000 & -2.56 \\
Sea Point & 40000 & 0.00\\
Sea Point & 50000 & 1.46 \\

@@

<!-- \def\tiny{\@setfontsize\tiny{10pt}{11pt}} -->
\begin{tiny}
\begin{center}
\setlength\tabcolsep{3pt}
\begin{longtable}{|r|r|p{2cm}|}
\caption{The cumulative intensity (°C xday) for the sites located within the Benguela upwelling system using the CMC dataset. The site column gives the name of the site. The distance column gives the distance from the coastline as seen in Fig 1.} \\

@@

Lamberts Bay & 10000 & 3.28725 \\
Lamberts Bay & 20000 & 2.92200 \\
Lamberts Bay & 30000 & 2.92200 \\
Lamberts Bay & 40000 & 2.55675 \\
Lamberts Bay & 50000 & 1.82625 \\
Port Nolloth & 10000 & 2.55675 \\
Port Nolloth & 20000 & 2.55675 \\
Port Nolloth & 30000 & 1.46100 \\
Port Nolloth & 40000 & 1.09575 \\
Port Nolloth & 50000 & 1.09575 \\
Saldanha Bay & 10000 & 3.28725 \\
Saldanha Bay & 20000 & 4.38300 \\
Saldanha Bay & 30000 & 4.01775 \\
Saldanha Bay & 40000 & 2.92200 \\
Saldanha Bay & 50000 & 2.92200 \\
Sea Point & 10000 & 3.28725 \\
Sea Point & 20000 & 3.65250 \\
Sea Point & 30000 & 4.01775 \\
Sea Point & 40000 & 3.28725 \\
Sea Point & 50000 & 2.19150 \\

@@

Lamberts Bay & 1.09575 \\
Port Nolloth & 1.09575 \\
Saldanha Bay & 0.36525 \\
Sea Point & 1.09575 \\
